Comparison and Evaluation of Popular Syntax Highlighting Themes in Terms of Color Correlated Temperature Values

### 2022-04-27 doc/manuscript.tex
.

\csvnames{themeccts}{
  analyze=\Xanalyze,
  fontface=\Xfontface,%
  fontsize=\Xfontsize,%
  language=\Xlanguage,%
  theme=\Xtheme,%
  cct=\Xcct,%
  cctbg=\Xcctbg,%
  diff65=\Xdiff,%
}

\begin{table}[H]
	\csvreader[%
		themeccts,%
		filter ifthen=\equal{\Xanalyze}{dark},%
		centered tabular=llll,%
		table head=\multicolumn{4}{c}{}\\\toprule
    Theme & $CCT_{avg}$ (K) & $CCT_{bg}$ (K) & D65 deviation (\%)\\\midrule,%
		late after line=\\, late after last line=\\\bottomrule%
	]{%
		./data/themes-by-cct.csv%
	}{}{%
    \Xtheme & \Xcct & \Xcctbg & \Xdiff%
	}

@@

\begin{table}[H]
	\csvreader[%
		themeccts,%
		filter ifthen=\equal{\Xanalyze}{light},%
		centered tabular=llll,%
		table head=\multicolumn{4}{c}{}\\\toprule
    Theme & $CCT_{avg}$ (K) & $CCT_{bg}$ (K) & D65 deviation (\%)\\\midrule,%
		late after line=\\, late after last line=\\\bottomrule
	]{%
		./data/themes-by-cct.csv%
	}{}{%
    \Xtheme & \Xcct & \Xcctbg & \Xdiff%
	}

@@

@@

\begin{figure}[htbp]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tabledark}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      xmin=0,
      width=0.8\textwidth,
      y=5mm,
    ]
      \addplot table[x=ccts,y=index] {\tabledark};
      \draw[thin,dashed] (axis cs: 6500,0) -- (axis cs: 6500,15.8) node[anchor=west, yshift=-210]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{CCT value comparison of dark themes}
  \label{fig:dark-compare}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tablelight}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      xmin=0,
      width=0.8\textwidth,
      y=5mm,
    ]
      \addplot [fill=red!30!white] table[x=ccts,y=index] {\tablelight};
      \draw[thin,dashed] (axis cs: 6500,0) -- (axis cs: 6500,15.8) node[anchor=west, yshift=-210]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{CCT value comparison of light themes}
  \label{fig:light-compare}
\end{figure}

>>>>

\csvnames{themeccts}{
  analyze=\Xanalyze,
  fontface=\Xfontface,%
  fontsize=\Xfontsize,%
  language=\Xlanguage,%
  theme=\Xtheme,%
  average_cct=\Xaveragecct,%
  average_cct_without_background=\averagecctwithoutbackground,%
  background_cct=\Xbackgroundcct,%
  diff65=\Xdiff,%
}

\begin{table}[H]
	\csvreader[%
		themeccts,%
		filter ifthen=\equal{\Xanalyze}{dark},%
		centered tabular=llll,%
		table head=\multicolumn{4}{c}{}\\\toprule
    Theme & $CCT_{avg}$ (K) & $CCT_{bg}$ (K) & D65 deviation (\%)\\\midrule,%
		late after line=\\, late after last line=\\\bottomrule%
	]{%
		./data/themes-by-cct.csv%
	}{}{%
    \Xtheme & \Xaveragecct & \Xbackgroundcct & \Xdiff%
	}

@@

\begin{table}[H]
	\csvreader[%
		themeccts,%
		filter ifthen=\equal{\Xanalyze}{light},%
		centered tabular=llll,%
		table head=\multicolumn{4}{c}{}\\\toprule
    Theme & $CCT_{avg}$ (K) & $CCT_{bg}$ (K) & D65 deviation (\%)\\\midrule,%
		late after line=\\, late after last line=\\\bottomrule
	]{%
		./data/themes-by-cct.csv%
	}{}{%
    \Xtheme & \Xaveragecct & \Xbackgroundcct & \Xdiff%
	}

@@

\begin{table}[H]
	\csvreader[%
		cct-descriptive,%
		centered tabular=lllll,%
		table head=\multicolumn{5}{c}{}\\\toprule
		Theme & Mean (K) & Std (K) & Min (K) & Max (K) \\\midrule,%
		late after line=\\, late after last line=\\\bottomrule%
	]{%
		./data/themes-statswobg.csv%
	}{}{%
		\Xtheme & \Xmean & \Xstd & \Xmin & \Xmax %
	}

	\caption{Theme descriptive statistics taking the background CCT as 6500 K}
	\label{tab:descriptive}
\end{table}

@@

\begin{figure}[htbp]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tabledark}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      xmin=0,
      width=0.8\textwidth,
      y=5mm,
    ]
      \addplot table[x=average_ccts,y=index] {\tabledark};
      \draw[thin,dashed] (axis cs: 6500,0) -- (axis cs: 6500,15.8) node[anchor=west, yshift=-210]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{CCT value comparison of dark themes}
  \label{fig:dark-compare}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tablelight}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      xmin=0,
      width=0.8\textwidth,
      y=5mm,
    ]
      \addplot [fill=red!30!white] table[x=average_ccts,y=index] {\tablelight};
      \draw[thin,dashed] (axis cs: 6500,0) -- (axis cs: 6500,15.8) node[anchor=west, yshift=-210]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{CCT value comparison of light themes}
  \label{fig:light-compare}
\end{figure}
